---
title: "Garcia Program Description"
author: "Randy Peterson"
date: "May 8, 2018"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:/zWork/ctc-psc/GarciaExampleMay2018/") #set root directory
library(knitr)
```

## What you will learn in this presentation

- How to use github
- How to use R
- How to compute MRE's in R
- How to compute CYER's in R

## Downloading requisite files directly from github

## Downloading requisite files from github via R

install.packages("pkgbuild") # pkgbuild is not available (for R version 3.5.0)
install.packages("devtools") # make sure you have the latest version from CRAN
library(devtools) # load package
devtools::install_github("r-lib/pkgbuild") # install updated version of pkgbuild from GitHub
library(pkgbuild) # load package
find_rtools() # should be TRUE, assuming you have Rtools 3.5
devtools::install_github("eriqande/rubias")
installed.packages()["rubias", "Version"]  # must be "0.1.0.900" in order to handle haploid data
library(rubias)  # load package and use!

## MRE Calculations

- What you'll need

ERA output
Fishery lookup file
Escapement data
Stock lookup file
R functions

- Options

## Load R functions

```{r echo = TRUE}
 source("Code/GarciaFunLibrary.R")
```

## Reading ERA output into R

```{r echo = TRUE}
 #Read in HRJ files in a directory
  by=readHRJdir(userDir="Data/", nFisheries=79, 
                straysinescap=TRUE, Age6="include")
 #Convert to CY layout
  cy=convertHRJ_BYtoCY(x=by)
 #Convert HRJ from R to Access format
  z.cy=convertHRJ_RtoAccess(x=cy, writeCSV=FALSE, userDir=NULL)
 #add the 'preferred' table to the Access format
  z.cy = addPTableHRJ(x=z.cy, hrjclass = "Access")
```

## readHRJdir()
```{r  results = "hide"}
readHRJdir(userDir="Data/", nFisheries=79, 
                straysinescap=TRUE, Age6="include")
```

## convertHRJ_BYtoCY()
```{r  results = "hide"}
convertHRJ_BYtoCY(x=by)
```

## convertHRJ_RtoAccess()
```{r  results = "hide"}
convertHRJ_RtoAccess(x=cy, writeCSV=FALSE, userDir=NULL)
```

## convertHRJ_RtoAccess()
```{r  results = "hide"}
addPTableHRJ(x=z.cy, hrjclass = "Access")
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

